Real World Manuscript Analyses

### 2022-06-02 RWE/RWE Manuscript analyses_.Rmd
Update

```{r library}
library(tidyverse)
library(lubridate)
library(ggplot2)
library(gtsummary)
library(labelled)
library(DescTools)
library(patchwork)
library(ggbreak)
library(survival)
library(survminer)
```

```{r load}
# path <- fs::path("","Volumes","Peres_Research", "Myeloma", "Cytopenias", "MM_CARTcell_cytopenia")
# path <- getwd()
MM_cart <-
  readxl::read_xlsx(
    "/Users/colinccm/Documents/GitHub/Peres/MM_CARTcell_cytopenia/RWE/FINAL 4.13.22 ASCO 2022 Myeloma CAR-T SOC Outcomes Spreadsheet.xlsx",
                    skip = 1, n_max = 198
                    ) %>% 
  rename(patient_id = `PT Identifier (DO NOT USE PHI)`)
```

>>>>

```{r library}
library(here)
library(tidyverse)
library(lubridate)
library(ggplot2)
library(gtsummary)
library(labelled)
library(DescTools)
library(patchwork)
library(ggbreak)
library(survival)
library(survminer)
```

```{r load}
MM_cart <-
  readxl::read_xlsx(paste0(here(), "/RWE/FINAL 4.13.22 ASCO 2022 Myeloma CAR-T SOC Outcomes Spreadsheet.xlsx"),
                    skip = 1, n_max = 198
                    ) %>% 
  rename(patient_id = `PT Identifier (DO NOT USE PHI)`)
```
